Title

### 2023-06-10 main.tex
.
Revision

Since their inception, quantum computers were proposed as powerful tools for the simulation of quantum systems,
with a recent particular interest in simulating the evolution of open systems, 
which are described by the theory of quantum channels~\cite{cleve,Zanetti,Xin,Wei}. \tbnote{Cita a Andrea}
{\color{purple} For example, this has been done using optical arrangements
to study the emergence of multipartite entanglement \cite{Andrea,Andrea_AD}.}
Among the various types of quantum channels for a system of qubits, 
Pauli channels hold special significance due to their simplicity 
and relevance in the context of quantum computing~\cite{Zbigniew,geometry}, 
as they serve as effective models for the noise affecting quantum devices~\cite{Flammia,Fawzi}.

On the other hand, we shall also work with parametrized quantum circuits, that is,  
a quantum circuit in which some of the operations depend on a variable parameter~\cite{cerezo}. 
The investigation of parametrized quantum
circuits holds extensive importance, 
as they find applications in quantum machine learning~\cite{Benedetti}
and describe general quantum transformations dependent on a parameter. Substantial research has been 
devoted to enhancing the efficiency of these circuits~\cite{Watanabe,Rasmussen}.

@@

Expanding beyond discrete Pauli channels,
we introduce the concept of Pauli dynamical maps, 
which are defined as a continuous parametrization of
$N$-qubit Pauli channels. 
Consequently, we adapt the algorithm developed for Pauli channels 
to accommodate these dynamical maps by employing a 
parametrized quantum circuit. 
We contribute to the body of work related to parametrized quantum circuits by establishing theorem \ref{theorem2}.
This theorem outlines the types of transformations that 
can be done using a parametrized quantum circuit with the condition that only one
 single-qubit operation in the circuit may depend on the parameter.
We explicitly find the mathematical conditions for these types of
transformations and conclude about which 
Pauli dynamical maps can be done with them.

The paper is organized as follows: In section \ref{sec: Pauli Channels} 
we give the definition of quantum channels and focus particularly on Pauli channels for systems of
$N$ qubits. 
In section \ref{sec: Circuit for a Pauli Channel} we show the proposed circuit 
to implement a Pauli channel of $N$ qubits in a quantum computer. 
Furthermore, we simulate it on IBM’s computers for the special case of $N=1$
and obtain the fidelity of this implementation.  
In section \ref{sec: 1PR Circuits} we shift our focus to parametrized quantum circuits with the goal of
generalizing the circuit for Pauli channels to one for Pauli dynamical maps. 
We introduce theorem \ref{theorem2} to establish what operations can be done with a 
parametrized circuit that uses only one single-qubit operation dependent on the parameter.
Finally, in section \ref{sec: 1PR circuit for a Pauli map} 
we apply this theorem for the circuit of Pauli dynamical
maps and show a couple of maps that fulfill the theorem's conditions.

@@

In this work, we have undertaken the study of Pauli channels on systems of $N$ qubits, 
proposing an algorithm capable of implementing them on a quantum computer
with the assistance of $2N$ ancilla qubits.
 By running this algorithm on one of IBM's quantum computers, 
we observed that the fidelity of the simulated channels was highest for those 
closely resembling the totally depolarizing channel, 
and decreased as the channels approached unitary behavior. 
This performance can be attributed to the limitations and susceptibility to errors 
inherent in current quantum computers. 
Furthermore, being as general as it is,
the algorithm isn’t efficient for unitary channels, 
which can be done in a much simpler manner.

Additionally, we extended our investigation 
to encompass Pauli dynamical maps by leveraging the concept of a parametrized quantum circuit. 
Through this extension, we determined the mathematical conditions under which a
parametrized quantum circuit requires only one single-qubit 
rotation dependent on the parameter. Notably, theorem \ref{theorem2} establishes these
 conditions as applicable to any parametrized quantum circuit, 
 providing a general framework to describe the type of algorithms achievable using 
only one single-qubit parametrized rotation.
% }}}
\section{Supporting information} % {{{

\tbnote{Ver qué se debe de poner aquí según el template y también arreglar las imágenes de acuerdo a él.}
% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
% \paragraph*{S1 Fig.}
% \label{S1_Fig}
% {\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).
% 
% \paragraph*{S2 Fig.}
% \label{S2_Fig}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 File.}
% \label{S1_File}
% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Video.}
% \label{S1_Video}
% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Appendix.}
% \label{S1_Appendix}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Table.}
% \label{S1_Table}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% }}}
\section{Acknowledgments} % {{{
Support by projects CONACyT 285754, 254515 and UNAM-PAPIIT IG100518, IG101421 is
acknowledged.

>>>>

Since their inception, quantum computers were proposed as powerful tools for the simulation of quantum systems,
with a recent particular interest in simulating the evolution of open quantum systems, 
which are described by the theory of quantum channels~\cite{cleve,Zanetti,Xin,Wei}. \tbnote{Cita a Andrea}
{\color{purple} For example, this has been done using optical arrangements
to study the emergence of multipartite entanglement \cite{Andrea,Andrea_AD}.}
Among the various types of quantum channels for a system of qubits, 
Pauli channels hold special significance due to their simplicity 
and relevance in the context of quantum computing~\cite{Zbigniew,geometry}, 
as they serve as effective models for the noise affecting quantum devices~\cite{Flammia,Fawzi}.

Additionally , we shall also work with parametrized quantum circuits, that is,  
quantum circuits in which some of the operations depend on variable parameters~\cite{cerezo}. 
These circuits play an important 
part in applications such as quantum machine learning~\cite{Benedetti}
and describing general quantum transformations dependent on parameters. Substantial research has been 
devoted to enhancing the efficiency of these circuits~\cite{Watanabe,Rasmussen}.

@@

Expanding beyond discrete Pauli channels,
we introduce the concept of Pauli dynamical maps, 
defined as a continuous parametrization of
$N$-qubit Pauli channels. 
We adapt the algorithm developed for Pauli channels 
to accommodate these dynamical maps by employing a 
parametrized quantum circuit. 
Furthermore, we contribute to the body of work related to parametrized quantum circuits by establishing theorem \ref{theorem2},
which outlines the types of transformations that 
can be done using a parametrized circuit with the condition that only one
 single-qubit operation in the circuit may depend on the parameter.
We explicitly find the mathematical conditions for these types of
transformations and conclude about which 
Pauli dynamical maps can be done with them.

The paper is organized as follows: In section \ref{sec: Pauli Channels} 
we provide  the definition of quantum channels and focus specifically on Pauli channels for systems of
$N$ qubits. 
In section \ref{sec: Circuit for a Pauli Channel} we present  the proposed circuit 
for implementing a Pauli channel of $N$ qubits in a quantum computer. 
Furthermore, we simulate it on IBM’s computers for the special case of $N=1$
and obtain the fidelity of this implementation.  
Section \ref{sec: 1PR Circuits} shifts the focus to parametrized quantum circuits, 
aiming to generalize the circuit for Pauli channels to accommodate Pauli dynamical maps. 
We introduce theorem \ref{theorem2} to determine the operations that can be 
performed using a parametrized circuit 
with only one single-qubit operation dependent on the parameter.
Finally, in section \ref{sec: 1PR circuit for a Pauli map} 
we apply this theorem for the circuit of Pauli dynamical
maps and show a couple of maps that fulfill the theorem's conditions.

@@

In this study, we focused on the analysis of Pauli channels in N-qubit systems and
developed an algorithm to implement them on a quantum computer.
 By running this algorithm on one of IBM's quantum computers, 
we observed that the fidelity of the simulated channels was highest for those 
closely resembling the totally depolarizing channel, 
and decreased as the channels approached unitary behavior. 
This performance can be attributed to the limitations and susceptibility to errors 
inherent in current quantum computers. 
Furthermore, being as general as it is,
the algorithm isn’t efficient for unitary channels, 
which can be done in a much straightforward manner.

Additionally, we extended our investigation 
to encompass Pauli dynamical maps by leveraging the concept of a parametrized quantum circuit. 
Through this extension, we determined the mathematical conditions under which a
parametrized quantum circuit requires only one single-qubit 
rotation dependent on the parameter. Notably, theorem \ref{theorem2} establishes these
 conditions as applicable to any parametrized quantum circuit, 
 providing a general framework to describe the type of algorithms achievable using 
only one single-qubit parametrized rotation.
% }}}

%\section{Supporting information} % {{{

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
% \paragraph*{S1 Fig.}
% \label{S1_Fig}
% {\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).
% 
% \paragraph*{S2 Fig.}
% \label{S2_Fig}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 File.}
% \label{S1_File}
% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Video.}
% \label{S1_Video}
% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Appendix.}
% \label{S1_Appendix}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Table.}
% \label{S1_Table}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% }}}
\section{Acknowledgments} % {{{
Support by projects CONACyT 285754, 254515 and UNAM-PAPIIT IG100518, IG101421 is
acknowledged.
